---
title: "Summary of IndyUseR Survey (Jan 2019)"
output: html_document
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```
This survey had only 13 responses. So it is just as easy to look through the responses from the [raw csv file](IndyUseRSurvey.csv). Also, google forms itself summarizes the responses. The purpose of creating the summary using R is to learn to process the format in which google forms stores survey data using R. 

The following chunk loads the survey data
```{r}
# Load libraries
library(tidyverse)
library(gt)

# load survey data
surveydf = read_csv("IndyUseRSurvey.csv")
surveydf
```
This format is not convenient to work with. Each respondents answers are across the row. Also, multiple responses to a single question appear in the same field separated by semicolon. Next, I convert the data to a tall format since that is easier to work with.I used the list-column and unnest feature to separate multiple responses to a single question into individual rows.
```{r}
# gather all questions/answers in tall format
surveydf = surveydf %>% select(-Timestamp) %>% mutate(id = seq(1, nrow(surveydf)))
# split responses where more than one response is given to a question
surveydf_g = surveydf %>% gather(question, answer, -id)
surveydf_g = surveydf_g %>% mutate(anssplit = strsplit(answer,";")) %>% unnest(anssplit)
surveydf_g = surveydf_g %>% mutate(anssplit = str_wrap(anssplit, 30))

# question list
questions = surveydf_g %>% distinct(question)
questions = questions$question

surveydf_g
```

```{r}
# function to get bar plot for multiple choice questions
getbarplot = function(quest) {
  p = ggplot(surveydf_g %>% filter(question == quest) %>% count(anssplit)) + 
    geom_col(aes(x = fct_reorder(anssplit, n), y = n), width = 0.5, fill = "lightblue") + 
    xlab("") + ylab("# responses") + 
    coord_flip() + theme_bw() + ggtitle(str_wrap(quest))
  return(p)
}
```

Next, we get the counts of choices for the multiple choice questions
```{r}
barplotq = c(1, 2, 3, 4, 6, 7, 8, 10, 12)
for(i in barplotq) {
  p = getbarplot(questions[i])
  print(p)
}
```

Next, we list the reponses to open ended questions and use the awesome new **gt** package to format it nicely
```{r}
openrespq = surveydf_g %>% filter(question %in% questions[c(5, 9, 11, 13, 14)]) %>% 
              filter(!is.na(anssplit)) %>% select(question, anssplit) %>% 
              rename(response = anssplit)
openrespq %>% mutate(dummy = "         ") %>% gt(rowname_col = "dummy", groupname_col = "question")
```

## Session Info

```{r}
sessionInfo()
```
